Nabi - A Preventative Solution Against JavaScript and Scriptless Tabnabbing Attacks

### 2015-05-05 paper/paper.tex
changes to conclusion

However, the scriptless form of the attack can still successfully occur. The current build of Nabi does not detect or block meta tag redirections and

@@

>>>>

@@

We have devleoped a system to block tabnabbing attacks that still allows the user to retain most of the javascript functionality they need to securly browse the internet while without just only detecting and alerting the user.
